AGEAS: Automated Machine Learning based Genetic Regulatory Element Extraction System

### 2022-10-16 docs/manuscript/main.tex
v0.0.v1a9
minor updates

\author[1,2,*1,+]{Jack Yu}
% \author[1,2,*1]{Jack Yu}
\author[2,+]{Masayoshi Nakamoto}
\author[1,*2,+]{Jiawang Tao}

% \author[2,+]{Derek Author}
\affil[1]{Center for Health Research, Guangzhou Institutes of Biomedicine and Health, Chinese Academy of Sciences, Guangzhou 510530, China}
\affil[2]{Shenzhen Mozhou Technology Co., Ltd, Shenzhen, China}
% \affil[2]{Affiliation, department, city, postcode, country}
\affil[*1]{Correspondence: gyu17@alumni.jh.edu}
\affil[*2]{Correspondence: tao\_jiawang@gibh.ac.cn}

@@

\section*{Acknowledgement}
  We sincerely thank Cher Li and Jie Wang for inspiration; Augustine(Xiaoran) Yuan for reviewing and support.

>>>>

% \author[1,2,*1]{Jack Yu}
\author[1,+]{Masayoshi Nakamoto}
\author[2,*1,+]{Jiawang Tao}
\author[1,2,*2,+]{Jack Yu}

% \author[2,+]{Derek Author}
\affil[1]{Shenzhen Mozhou Technology Co., Ltd, Shenzhen, China}
\affil[2]{Center for Health Research, Guangzhou Institutes of Biomedicine and Health, Chinese Academy of Sciences, Guangzhou 510530, China}
% \affil[2]{Affiliation, department, city, postcode, country}
\affil[*1]{Correspondence: tao\_jiawang@gibh.ac.cn}
\affil[*2]{Correspondence: gyu17@alumni.jh.edu}

@@

\section*{Acknowledgement}
  We sincerely thank Cher Li and Jie Wang for inspiration; Augustine(Xiaoran) Yuan and Elizabeth Bania for reviewing and support.
